---
title: "HAR Machine Learning"
author: "Kennex Razon"
date: "December 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caret)
```

## The HAR Dataset
We start with the dataset. I run the code in different machines and some don't have internet connection so I had to comment out some of the file address.

Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.

Read more: http://groupware.les.inf.puc-rio.br/har#dataset#ixzz5Ycr9NiOI

We initially try to use all variables to try a generalized linear model. And we'll fail horribly when we do this. 

```{r}
df <- read.csv(file="D:/PraticalMachineLearning/PracticalMachineLearningRepo/trunk/pml-training.csv", header=TRUE, sep=",",na.strings = c("NA","",'#DIV/0!'))
df_test <- read.csv(file="D:/PraticalMachineLearning/PracticalMachineLearningRepo/trunk/pml-testing.csv", header=TRUE, sep=",",na.strings = c("NA","",'#DIV/0!'))

#df <- read.csv(file="C:/Users/DELL/Documents/PracticalMachineLearningRepo/trunk/pml-training.csv", header=TRUE, sep=",")

#df <- read.csv(file="D:/Desktop/PracticalMachineLearningRepo/trunk/pml-training.csv", header=TRUE, sep=",",na.strings = c("NA","",'#DIV/0!'))
#df_test <- read.csv(file="D:/Desktop/PracticalMachineLearningRepo/trunk/pml-testing.csv", header=TRUE, sep=",",na.strings = c("NA","",'#DIV/0!'))
```
First of all, a lot of the columns have non-numerics. Secondly there are also a lot of columns that have mostly NAs. Not to mention columns that only have values every so often. These columns usually had column names with `avg|max|min|var|amplitude|skewness|total|std|kurtosis|`. 

I'll look for those columns first then, subset the original `df` to `df1`. We'll also do the same for the testing data.
```{r har}



#a <- grep("avg|max|min|var|amplitude|skewness|total|std|kurtosis|classe",names(df),value=TRUE)
#a <- grep("avg|max|min|var|amplitude|std|classe",names(df),value=TRUE)
#df1 <- df[a]
df1 <- df
df1_test <- df_test
```
### Clean the data

One of our motivations for subsetting data this way is to remove the NAs. So we'll do that on our subsetted `df1` and store it in `df2`. We'll do the same with the testing data. 

Columns 1 to 6 contain data that is not relevant to our analysis.

```{r df1}
df1 <- df1[,(colSums(is.na(df1)) == 0)]
df1 <- df1[,7:ncol(df1)]
df2 <- df1

df1_test <- df1_test[,(colSums(is.na(df1_test)) == 0)]
df1_test <- df1_test[,7:ncol(df1_test)]
df2_test <- df1_test

#df2 <- data.frame(lapply(df2,as.numeric))
#df2 <- df2[,colSums(is.na(df2))<ncol(df2)]
#df2 <- df1[complete.cases(df1), ]
#b <- grep("max|min|amplitude",names(df2),value=TRUE)
#df2 <- data.frame(lapply(df2, function(x) { gsub("#DIV/0!", "NA", x)}))
#b <- names(df2)[1:ncol(df2)-1]
#df2[b] <- data.frame(lapply(df2[b],as.numeric))
#str(df2[b])

```

Initial runs showed problems in runtime. To reduce this at least for the building of this code, a very small subset of the data was used for testing. 

```{r fitting}

#trainDf<-createDataPartition(y=df2$classe,p=0.1,list=FALSE)
#training <- df2[trainDf,]
#testing <- df2[-trainDf,]

#trainingData <- training[,1:length(names(training))-1]
#trainingClass <- training[,length(names(training))]
set.seed(21)
```
### Classify

The training data `df2` is used to create a model also with cross validation.

```{r pressure, echo=FALSE}
modelFit <- train(classe ~ .,data=df2, method = 'rf', trControl = trainControl(method = "cv") )
modelFit
prediction1<- predict(modelFit,df2_test)
#plot(pressure)
```

### Trying different resampling methods
```{r}
#modelFit_cv <- train(trainingData,trainingClass,method = 'rpart', trControl = trainControl(method = "cv"))
#modelFit_cv
```

### Using Bootstrapping
```{r}
#modelFit_oob <- train(trainingData,trainingClass,method = 'cforest', trControl = trainControl(method = "oob"))
#modelFit_oob
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
